Supplementary material for: \nA comparison of single-cell trajectory inference methods: towards more accurate and robust tools

### 2018-11-12 manuscript/supplementary.Rmd
update supplementary

# Supplementary figures
```{r, results="asis"}
sfigs %>% pmap(dynbenchmark:::plot_fig, ref_type = "sfig") %>% modify(paste0, "\n\n") %>% walk(cat)
```

@@

```{r setup, include=FALSE}
# source(paste0(dynbenchmark::get_dynbenchmark_folder(), "/analysis/paper/setup.R"))
# 
# # knitr options
# knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
# knitr::opts_chunk$set(
#   collapse = TRUE,
#   warning = FALSE,
#   message = FALSE,
#   echo = FALSE,
#   comment = "#>",
#   fig.path = paste0(rprojroot::find_rstudio_root_file(), "/analysis/paper/.scratch/")
# )
# 
# list2env(read_rds(derived_file("sfigs_stables.rds", "paper")), environment())
```

```{r "supplementary", echo=FALSE, results='asis'}
# source(paste0(dynbenchmark::get_dynbenchmark_folder(), "/analysis/paper/sfigs_stables.R"))
```

>>>>

# Supplementary figures
```{r, results="asis"}
sfigs %>% 
  left_join(refs %>% select(ref_id, name), "ref_id") %>% 
  arrange(name) %>% 
  select(-name) %>% 
  pmap(dynbenchmark:::plot_fig, ref_type = "sfig") %>% modify(paste0, "\n\n") %>% walk(cat)
```

\clearpage

@@

\clearpage

# Supplementary note 1

```{r}
# dynbenchmark::knit_nest("../results/02-metrics/")
```
